Elicitation Complexity via Convex Piecewise Linear Loss Functions

### 2018-10-17 jessie-writeup/jessie-writeup.tex
meeting notes
Prep to merge
Small updates to writeup

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma$ be a nondegenerate elicitable property with a finite set of \jessie{full-dimensional} level sets \jessie{$\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$}.
%	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \preceq \Gamma$. 
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets, elicitability implies convex score $G$, i.e. differentiable a.e.}\raft{Confused by BR}

@@

\begin{proof}
	Showing the level sets of $\Gamma$ are subsets of the level sets of $\gamma$ is to show that $p \in \Gamma_r \implies \exists r' \in \R'$ so that $p \in \gamma_{r'}$ for all $p \in \Gamma_r$.

@@

  The following are equivalent:
  \begin{enumerate}
  \item There is a nondegenerate, finite property $\Gamma':\P\toto\R'$ such that there is an injection $\varphi:\R'\to\R$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$. (i.e. $\Gamma$ embeds finite $\Gamma'$)
  \item There is a finite set of full dimensional level sets of $\Gamma$ that union to $\P$.
  \item There is a finite set $\Theta \subseteq \strip(\Gamma)$ of full-dimensional level sets, such that: (a) $\bigcup_{\theta\in\Theta} \theta = \P$, (b) for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
  \item $\strip(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite and elicitable.

@@

\begin{proof}
First, we show $5 \iff 4$ then proceed in a cycle to show $1 \implies 3 \implies 2 \implies 6 \implies 5 \implies 1$.

@@

	\item[$5 \iff 4$] 
	We know $\trim(\Gamma) \subseteq \strip(\Gamma)$, and if $\strip(\Gamma)$ is finite, then any subset of $\strip(\Gamma)$ is finite.
	Thus we just show $5 \implies 4$.

	Consider $\trim(\Gamma)$ to be finite.
%	If $\Gamma$ is nonredundant, then we are finished, as $\Gamma \preceq \Gamma$ and would be nondegenerate and nonredundant, so we can say $\trim(\Gamma) = \strip(\Gamma)$.
	We know there is a nonredundant, nondegenerate $\Gamma' \preceq \Gamma$ so that $\strip(\Gamma') = \trim(\Gamma)$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
	We take $\Gamma'$ and $\R'$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
	We then want to show $\strip(\Gamma) = \strip(\Gamma') \bigcup S$, where $S$ is some finite set.
	Consider the level set $\Gamma_r$ for $r \in \R$.
	If $r \in \R'$, then $\Gamma_r \in \strip(\Gamma')$.
	If $r \not \in \R'$, then the level set $\Gamma_r$ has empty interior by construction of $\R'$.
	%\jessie{Need argument about how we can only have level sets on the boundary.}

	Since $\Gamma$ is elicitable, the score $G(p)$ is concave, thus differentiable almost everywhere in the probability space $\P$.
	Thus, every level set with nonempty interior has $|\partial G(p)| = |\Gamma(p)| = 1$ for all $p \in \inter{\theta}$, and there is then a report $r \in \R'$ so that $\theta \in \Gamma_r$.

	Thus, we concern ourselves with the case $|\partial G(p)| > 1$.
	%If $|\partial_p G(p)| = 1$ for some $p \in\theta$, then the interior $\inter{\theta} \neq \emptyset$, implying $r \in \R'$ by closure of level sets, so we must concern ourselves with the case $|\partial_p G(p)| > 1$.
	As subgradient sets are closed, there exists a finite set of full dimensional level sets $\{\theta_i\}_{i=1}^m$ in the $\epsilon$-ball around each $p \in \theta$ so that for any $p_i \in \inter{\theta_i}$, we observe $\partial G(p_i) \neq \partial G(p_j)$ for all $i \neq j$ and $\partial G(p_i) = \Gamma(p) = \{r_i\}$ for all $1 \leq i \leq m$.
	Additionally, as level sets are closed, we claim $p \in \Gamma_{r_i}$ for all $1 \leq i \leq m$.
	Therefore, $p \in \theta \implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \Gamma_{r'}$ for some $\{r_i\}_{i=1}^m \subseteq \R'$.
	As $\R'$ is finite, so is the power set $2^{\R'}$, so the set $S = \{\Gamma_r : r \in \R \setminus \R' \}$ is finite.
	Therefore $\strip(\Gamma) = \strip(\Gamma') \cup S$ is finite.

@@

%%% means taken out to reduce space and make the proof a loop
%%%\item [$2 \implies 1$]
%%%Consider $\trim(\Gamma) = \Theta$.
%%%$\Theta$ is then finite and a subset of strip by definition, and by Conjecture~\ref{conj:trim-full-dim}, every $\theta \in \Theta$ is full dimensional.
%%%Consider that $\trim(\Gamma) = \strip(\Gamma')$ for the property $\Gamma'$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and as $\Gamma'$ is nondegenerate, then for every $p \in \P$, there is a $\theta \in \Theta$ such that $p \in \theta$, so the union of the level sets is then equal to the distribution set $\P$.
%%%Additionally, as $\Gamma$ is elicitable, the optimal report is unique almost everywhere by concavity of the score $G$.
%%%Therefore, if $p \in \inter{\theta}$ and the optimal report $r_\theta$ is unique almost everywhere, then as there is an $\epsilon$-ball around $p$ where every for every $p'$ in the ball, $p' \in B(\epsilon, p)$, $\Gamma(p) = \Gamma(p')$.

@@

\item[$1 \implies 3$] 
Let the elicitable property $\Gamma$ embed some finite property $\gamma$.
Then since $\gamma$ is a finite set of level sets, and every level set of $\Gamma$ is a subset of a level set of $\gamma$ by Conjecture~\ref{conj:lev-sets-subsets}.

Consider the finite set $\R'$ to be the range of $\gamma$.

By Conjecture~\ref{conj:prec-if-embeds}, since $\Gamma$ embeds $\gamma$, we know that $\gamma \preceq \Gamma$, so $\Theta = \strip(\gamma) = \trim(\Gamma)$ is finite and every $\theta \in \Theta$ is full dimensional.
Since $\Gamma$ is elicitable, the optimal report $r_\theta \in \Gamma(p)$ is unique almost everywhere on $\P$ (by differentiability of the score $G$ almost everywhere).
Additionally, as $\gamma$ is nondegenerate, its level sets union to $\P$.

For each level set $\theta \in \Theta$, there is a unique optimal report $\{r_\theta \} = \Gamma(p)$ for all $p \in \inter{\theta}$ by the elicitability of $\Gamma$.
This can be seen by the differentiability of $G$ almost everywhere in $\P$, and thus uniqueness of $\Gamma(p)$ almost everywhere.
A convex level set with nonempty interior has positive measure, so if $r_\theta$ was not unique on the interior of $\theta$, the set where $r_\theta$ is not unique would have positive measure, contradicting elicitability of $\Gamma.$

Therefore the set $\Theta = \{\gamma_r : r \in \R' \} = \trim(\Gamma) \subseteq \strip(\Gamma)$ is a finite set of full dimensional level sets that union to $\P$ with a unique optimal report on the interior of each level set. 
\item[$3 \implies 2$] Trivial
\item[$2 \implies 6$]
Let $\Theta$ be a set of full-dimensional level sets of $\Gamma$ that union to $\P$.
First, we know $\Gamma$ is nondegenerate.

The $\Gamma'$ constructed in Conjecture~\ref{conj:gam-prime-exists} has a finite codomain $\R'$ since $\R'$ is the set defined by the unique optimal report defined on the interior of each level set.
Since there are only finitely many full-dimensional level sets, the set $\R'$ is finite.

We then know by definition of $\trim$ that since $\Gamma'$ is nonredundant, nondegenerate, and $\Gamma' \preceq \Gamma$, that $\strip(\Gamma') = \trim(\Gamma)$ is finite.

Therefore $\trim(\Gamma)$ is finite, and $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.

\item[$6 \implies 5$] Trivial
\item[$5 \implies 1$] Let $\trim(\Gamma)$ be finite.
Then there is a nondegenerate, nonredundant, finite property $\gamma$ so that $\{ \gamma_r : r \in \R' \} = \strip(\gamma) = \trim(\Gamma)$.

Then we want to show $\Gamma$ embeds $\gamma$.
Since we know $\card(\trim(\Gamma)) = \card(\R')$ is finite and $\trim(\Gamma)$ is a subset of the codomain of $\Gamma$, $\R$, then $\card(\R')) \leq \card(\R)$ \jessie{$?= \card(\reals^d)$... again assuming $\R$ is a \emph{convex} subset of $\reals^d$}, there is an injection $\varphi : \R' \to \R$ from Folland Section 0.

Consider some $r \in \gamma(p)$.
Since there is an injection $\varphi$ from $\R' \to \R$, then $r \in \gamma(p) \implies \varphi(r) \in \varphi(\gamma(p)) = \Gamma(p)$.
\jessie{Hand wavy...}

Now consider $\varphi(r) \in \Gamma(p)$.
Take the right inverse (well-defined since $\varphi$ is an injection) and observe that $r \in \varphi^{-1}(\Gamma(p) \cap \R') = \gamma(p)$ since $\gamma$ is nondegenerate.

Therefore, $5 \implies 1$.

@@

\begin{conjecture}\label{conj:prec-if-embeds}
	If the elicitable property $\Gamma$ embeds the nondegenerate \jessie{elicitable?} finite $\gamma$, then $\gamma \preceq \Gamma$ and $\trim(\Gamma) = \strip(\gamma)$.
\end{conjecture}
\begin{proof}

	By assumption, $\gamma$ is nongenerate.

	To show $\gamma \preceq \Gamma$, we know that since $\Gamma$ embeds $\gamma$, there is an injection $\varphi : \R' \to \R$ so that $r' \in \gamma(p) \iff \varphi(r') \in \Gamma(p)$.
	Therefore, we know for all $r' \in \R'$ that $\varphi(r') \in \R$, therefore, $\varphi(\R') \subseteq \R$.
	As $\varphi(\R') \subseteq \R$ and $\gamma$ is nondegenerate, we know that for all $r \in \R'$, we know $\gamma \preceq \Gamma$.
	Therefore, $\gamma(p) = \Gamma(p) \cap \R'$

	Finally, we show $\gamma$ is nonredundant. 
	For contradiction, suppose there are two reports $r, r' \in \R'$ so that $r \neq r'$ and $\gamma_r \subseteq \gamma_{r'}$.
	Since $\Gamma$ embeds $\gamma$, for any $p \in \P$, we know $p \in \gamma_r \iff p \in \Gamma_{\varphi(r)}$.
	Therefore, $\Gamma_{\varphi(r)} \subseteq \Gamma_{\varphi(r')}$, where $\varphi(r) \neq \varphi(r')$ as $\varphi$ is an injection.

	Since $\gamma_r \subseteq \gamma_{r'}$, then $\gamma_r \cap \gamma_{r'} = \gamma_r$.
	We know $p \in \gamma_r$ and $\gamma_{r'} \iff p \in \Gamma_{\varphi(r)}$ and $\Gamma_{\varphi(r')} \iff p \in \Gamma_{\lambda \varphi(r) + (1-\lambda) \varphi(r')}$ for all $\lambda \in [0,1]$ by elicitability of $\Gamma$ and closure of subgradient sets of $G_{\Gamma}$.
	Since the reals are (uncountably) infinite, we then contradict the finiteness of $\gamma$.
	Therefore, we conclude $\gamma$ must be nonredundant.
	\jessie{I don't think this is correct... I think we need convexity of $\R$ in order to claim this, which we technically don't assume.}

>>>>

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma$ be a nondegenerate elicitable property with a finite set of \jessie{full-dimensional} level sets \jessie{$\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$}.
	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \preceq \Gamma$. 
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets, elicitability implies convex score $G$, i.e. differentiable a.e.}\raft{Confused by BR}

@@

\begin{proof}
	Showing the level sets of $\Gamma$ are subsets of the level sets of $\gamma$ is to show that $p \in \Gamma_r \implies \exists r' \in \R'$ so that $p \in \gamma_{r'}$ for all $p \in \Gamma_r$.
    \raf{Want to say $\forall r$ $\exists r'$ $p \in \Gamma_r \implies p \in \gamma_{r'}$.}

@@

  The following are equivalent:
  \begin{enumerate}
  \item There is a nondegenerate, finite property $\gamma:\P\toto\R'$ such that there is an injection $\varphi:\R'\to\R$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$. (i.e. $\Gamma$ embeds finite $\gamma$)
  \item There is a finite set of full dimensional level sets of $\Gamma$ that union to $\P$.
  \item There is a finite set $\Theta \subseteq \strip(\Gamma)$ of full-dimensional level sets, such that: (a) $\bigcup_{\theta\in\Theta} \theta = \P$, (b) for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
  \item $\strip(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite and elicitable.

@@

\begin{proof}
\jessie{Old: First, we show $5 \iff 4$ then proceed in a cycle to show $1 \implies 3 \implies 2 \implies 6 \implies 5 \implies 1$.}
We proceed in a cycle to show $5 \implies 1 \implies 6 \implies 2 \implies 3 \implies 4 \implies 5$.

@@

%%% Commented out 10/17/18
%%%	\item[$5 \iff 4$] 
%%%	We know $\trim(\Gamma) \subseteq \strip(\Gamma)$, and if $\strip(\Gamma)$ is finite, then any subset of $\strip(\Gamma)$ is finite.
%%%	Thus we just show $5 \implies 4$.
%%%	
%%%	Consider $\trim(\Gamma)$ to be finite.
%%%%	If $\Gamma$ is nonredundant, then we are finished, as $\Gamma \preceq \Gamma$ and would be nondegenerate and nonredundant, so we can say $\trim(\Gamma) = \strip(\Gamma)$.
%%%	We know there is a nonredundant, nondegenerate $\Gamma' \preceq \Gamma$ so that $\strip(\Gamma') = \trim(\Gamma)$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
%%%	We take $\Gamma'$ and $\R'$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
%%%	We then want to show $\strip(\Gamma) = \strip(\Gamma') \bigcup S$, where $S$ is some finite set.
%%%	Consider the level set $\Gamma_r$ for $r \in \R$.
%%%	If $r \in \R'$, then $\Gamma_r \in \strip(\Gamma')$.
%%%	If $r \not \in \R'$, then the level set $\Gamma_r$ has empty interior by construction of $\R'$.
%%%	%\jessie{Need argument about how we can only have level sets on the boundary.}
%%%	
%%%	Since $\Gamma$ is elicitable, the score $G(p)$ is concave, thus differentiable almost everywhere in the probability space $\P$.
%%%	Thus, every level set with nonempty interior has $|\partial G(p)| = |\Gamma(p)| = 1$ for all $p \in \inter{\theta}$, and there is then a report $r \in \R'$ so that $\theta \in \Gamma_r$.
%%%	
%%%	Thus, we concern ourselves with the case $|\partial G(p)| > 1$.
%%%	%If $|\partial_p G(p)| = 1$ for some $p \in\theta$, then the interior $\inter{\theta} \neq \emptyset$, implying $r \in \R'$ by closure of level sets, so we must concern ourselves with the case $|\partial_p G(p)| > 1$.
%%%	As subgradient sets are closed, there exists a finite set of full dimensional level sets $\{\theta_i\}_{i=1}^m$ in the $\epsilon$-ball around each $p \in \theta$ so that for any $p_i \in \inter{\theta_i}$, we observe $\partial G(p_i) \neq \partial G(p_j)$ for all $i \neq j$ and $\partial G(p_i) = \Gamma(p) = \{r_i\}$ for all $1 \leq i \leq m$.
%%%	Additionally, as level sets are closed, we claim $p \in \Gamma_{r_i}$ for all $1 \leq i \leq m$.
%%%	Therefore, $p \in \theta \implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \Gamma_{r'}$ for some $\{r_i\}_{i=1}^m \subseteq \R'$.
%%%	As $\R'$ is finite, so is the power set $2^{\R'}$, so the set $S = \{\Gamma_r : r \in \R \setminus \R' \}$ is finite.
%%%	Therefore $\strip(\Gamma) = \strip(\Gamma') \cup S$ is finite. 
%%%End commented out 10/17/18

@@

%%% means taken out to reduce space and make the proof a loop 10/12/18
%%%\item [$2 \implies 1$]
%%%Consider $\trim(\Gamma) = \Theta$.
%%%$\Theta$ is then finite and a subset of strip by definition, and by Conjecture~\ref{conj:trim-full-dim}, every $\theta \in \Theta$ is full dimensional.
%%%Consider that $\trim(\Gamma) = \strip(\Gamma')$ for the property $\Gamma'$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and as $\Gamma'$ is nondegenerate, then for every $p \in \P$, there is a $\theta \in \Theta$ such that $p \in \theta$, so the union of the level sets is then equal to the distribution set $\P$.
%%%Additionally, as $\Gamma$ is elicitable, the optimal report is unique almost everywhere by concavity of the score $G$.
%%%Therefore, if $p \in \inter{\theta}$ and the optimal report $r_\theta$ is unique almost everywhere, then as there is an $\epsilon$-ball around $p$ where every for every $p'$ in the ball, $p' \in B(\epsilon, p)$, $\Gamma(p) = \Gamma(p')$.

@@

%%%Commented out 10/17/18
%%%\item[$1 \implies 3$] 
%%%Let the elicitable property $\Gamma$ embed some finite property $\gamma$.
%%%Then since $\gamma$ is a finite set of level sets, and every level set of $\Gamma$ is a subset of a level set of $\gamma$ by Conjecture~\ref{conj:lev-sets-subsets}.
%%%
%%%Consider the finite set $\R'$ to be the range of $\gamma$.
%%%
%%%By Conjecture~\ref{conj:prec-if-embeds}, since $\Gamma$ embeds $\gamma$, we know that $\gamma \preceq \Gamma$, so $\Theta = \strip(\gamma) = \trim(\Gamma)$ is finite and every $\theta \in \Theta$ is full dimensional.
%%%Since $\Gamma$ is elicitable, the optimal report $r_\theta \in \Gamma(p)$ is unique almost everywhere on $\P$ (by differentiability of the score $G$ almost everywhere).
%%%Additionally, as $\gamma$ is nondegenerate, its level sets union to $\P$.
%%%
%%%For each level set $\theta \in \Theta$, there is a unique optimal report $\{r_\theta \} = \Gamma(p)$ for all $p \in \inter{\theta}$ by the elicitability of $\Gamma$.
%%%This can be seen by the differentiability of $G$ almost everywhere in $\P$, and thus uniqueness of $\Gamma(p)$ almost everywhere.
%%%A convex level set with nonempty interior has positive measure, so if $r_\theta$ was not unique on the interior of $\theta$, the set where $r_\theta$ is not unique would have positive measure, contradicting elicitability of $\Gamma.$
%%%
%%%Therefore the set $\Theta = \{\gamma_r : r \in \R' \} = \trim(\Gamma) \subseteq \strip(\Gamma)$ is a finite set of full dimensional level sets that union to $\P$ with a unique optimal report on the interior of each level set. 
%%%\item[$3 \implies 2$] Trivial
%%%\item[$2 \implies 6$]
%%%Let $\Theta$ be a set of full-dimensional level sets of $\Gamma$ that union to $\P$.
%%%First, we know $\Gamma$ is nondegenerate.
%%%
%%%The $\Gamma'$ constructed in Conjecture~\ref{conj:gam-prime-exists} has a finite codomain $\R'$ since $\R'$ is the set defined by the unique optimal report defined on the interior of each level set.
%%%Since there are only finitely many full-dimensional level sets, the set $\R'$ is finite.
%%%
%%%We then know by definition of $\trim$ that since $\Gamma'$ is nonredundant, nondegenerate, and $\Gamma' \preceq \Gamma$, that $\strip(\Gamma') = \trim(\Gamma)$ is finite.
%%%
%%%Therefore $\trim(\Gamma)$ is finite, and $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.
%%%
%%%\item[$6 \implies 5$] Trivial
%%%End commented out 10/17/18

\item[$5 \implies 1$] Let $\trim(\Gamma)$ be finite.
Then there is a nondegenerate, nonredundant, finite property $\gamma$ so that $\{ \gamma_r : r \in \R' \} = \strip(\gamma) = \trim(\Gamma)$, and we take $\gamma$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
We want to show that $\Gamma$ embeds this property $\gamma$.
First, we know $\gamma$ is nondegenerate and finite by construction.

Since we know $\card(\trim(\Gamma)) = \card(\R')$ is finite and $\trim(\Gamma)$ is a subset of the codomain of $\Gamma$, $\R$, then $\card(\R')) \leq \card(\R)$ \jessie{$?= \card(\reals^d)$... again assuming $\R$ is a \emph{convex} subset of $\reals^d$}, there is an injection $\varphi : \R' \to \R$ from Folland Section 0.

Consider some $r \in \gamma(p)$.
Since there is an injection $\varphi$ from $\R' \to \R$, then $r \in \gamma(p) \implies \varphi(r) \in \varphi(\gamma(p)) \subseteq \Gamma(p) \implies \varphi(\gamma(p)) \in \Gamma(p)$.

Now consider $\trim(\Gamma) = \strip(\gamma)$.
Therefore, for every level set $\theta\in\trim(\Gamma)$, there is a corresponding level set $\theta' \in \strip(\gamma)$ so that $\theta = \theta'$.

For any $r \in \R$, consider the level set $\Gamma_r$, if $\Gamma_r \in \trim(\Gamma)$, then there is a corresponding $\gamma_{r'}$ so that $p \in \Gamma_r \implies p \in \gamma_{r'}$ as $\strip(\gamma) = \trim(\Gamma)$.

Now, if for some $r \in \R$, we observe $\Gamma_r \not \in \trim(\Gamma)$, we know $\Gamma_r$ is not full dimensional by Conjecture~\ref{conj:trim-full-dim}.
As level sets of elicitable properties are closed (Lemma~\ref{lem:closed-level-sets}), there is some other $\tilde r \in \R$ so that $\Gamma_{\tilde r} \in \trim(\Gamma)$ and $p \in \Gamma_r \implies p \in \Gamma_{\tilde r} \implies p \in \gamma_{r'}$ for some $r' \in \R'$ so that $\tilde r = \varphi(r')$.

Therefore, if $\trim(\Gamma)$ is finite, then $\Gamma$ embeds the finite, nondegenerate property $\gamma$ such that $\trim(\Gamma) = \strip(\gamma)$ .
Thus, $5 \implies 1$.

\item [$1 \implies 6$]
Since $\strip(\gamma) = \trim(\Gamma)$ by Conjecture~\ref{conj:prec-if-embeds} and $\gamma$ is finite, we know $\trim(\Gamma)$ is finite.
Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.

\item [$6 \implies 2$]
Since $\Gamma$ is non degenerate and every $\theta \in \trim(\Gamma)$ is full dimensional (Conjecture~\ref{conj:trim-full-dim}), it is clear that the union of the  (full-dimensional) level sets of $\trim(\Gamma)$ union to $\P$.

\item [$2 \implies 3$]
We know that (a.) is satisfied by assumption.
Since $\Gamma$ is elicitable, the convex score $G(p)$ corresponds to the optimal report set at a distribution $p$.
Since $G$ is convex, it is differentiable almost everywhere, so the optimal report is unique almost everywhere.
In the interior of a convex level set has positive measure, the optimal report on the interior of each level set must then be unique.

\item [$3 \implies 4$]
	We know there is a nonredundant, nondegenerate $\gamma \preceq \Gamma$ so that $\strip(\gamma) = \trim(\Gamma) = \Theta$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
	We take $\gamma$ and $\R'$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
	We then want to show $\strip(\Gamma) = \strip(\gamma) \bigcup S$, where $S$ is some finite set.
	Consider the level set $\Gamma_r$ for $r \in \R$.
	If $r \in \R'$, then $\Gamma_r \in \strip(\gamma)$.
	If $r \not \in \R'$, then the level set $\Gamma_r$ has empty interior by construction of $\R'$.

	Thus, we concern ourselves with the case $|\partial G(p)| > 1$.
	We know this only happens at lower dimensional level sets $\theta$ by assumption (since the optimal report is unique on the interior of level sets).
	Since $\theta$ is not full dimensional and there is only a finite set of full dimensional level sets, we know there is a finite set of full dimensional level sets $\{\theta_i\}_{i=1}^m$ in the $\epsilon$-ball around each $p \in \theta$ so that for any $p_i \in \inter{\theta_i}$, we observe $\partial G(p_i) \neq \partial G(p_j)$ for all $i \neq j$ and $\partial G(p_i) = \Gamma(p_i) = \{r_i\}$ for all $1 \leq i \leq m$.
	Additionally, as level sets are closed, we claim $p \in \Gamma_{r_i}$ for all $1 \leq i \leq m$.
	Therefore, $p \in \theta \implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \Gamma_{r'}$ for some $\{r_i\}_{i=1}^m \subseteq \R'$.
	As $\R'$ is finite, so is the power set $2^{\R'}$, so the set $S = \{\Gamma_r : r \in \R \setminus \R' \}$ is finite.
	Therefore $\strip(\Gamma) = \strip(\Gamma') \cup S$ is finite. 
	\jessie{Come back to this- should be esay-ish though.}

\item [$4 \implies 5$]
Since $\trim(\Gamma) \subseteq \strip(\Gamma)$, then the strip being finite implies the trim is finite.

@@

\begin{conjecture}\label{conj:prec-if-embeds}
	If the elicitable property $\Gamma$ embeds the nondegenerate finite $\gamma$, then $\gamma \preceq \Gamma$ and $\trim(\Gamma) = \strip(\gamma)$.
\end{conjecture}
\begin{proof}
	If we show $\gamma$ is nondegenerate, nonredundant, and $\gamma \preceq \Gamma$, then by definition of $\trim$, we conclude that $\trim(\Gamma) = \strip(\gamma)$.	
	By assumption, $\gamma$ is nongenerate.

	To show $\gamma \preceq \Gamma$, we know that since $\Gamma$ embeds $\gamma$, there is an injection $\varphi : \R' \to \R$ so that $r' \in \gamma(p) \iff \varphi(r') \in \Gamma(p)$.
	Therefore, we know for all $r' \in \R'$ that $\varphi(r') \in \R$, therefore, $\varphi(\R') \subseteq \R$.
	As $\varphi(\R') \subseteq \R$ and $\gamma$ is nondegenerate, we know that for all $p \in \P$, we know $\gamma(p) = \Gamma(p) \cap \varphi(\R')$.
	Therefore, $\gamma \preceq \Gamma$.

	Finally we know $\gamma$ is nonredundant since $\varphi$ is an injection.
	Thus, $\gamma_r \subseteq \gamma_{r'}$ for $r, r' \in \R'$ and $r \neq r$ implies that $\Gamma_{\varphi(r)} \subseteq \Gamma_{\varphi(r')}$.
	Since $\varphi$ is an injection, we know that $\varphi(r) \neq \varphi(r')$.
	Since $\gamma$ is finite and nondegenerate, at any distribution $p$, there are $1 \leq m \leq |\R'|$ reports in $\gamma(p)$.

	For contradiction, suppose there are two reports $r, r' \in \R'$ so that $r \neq r'$ and $\gamma_r \subseteq \gamma_{r'}$.
	Since $\Gamma$ embeds $\gamma$, for any $p \in \P$, we know $p \in \gamma_r \iff p \in \Gamma_{\varphi(r)}$.
	Therefore, $\Gamma_{\varphi(r)} \subseteq \Gamma_{\varphi(r')}$, where $\varphi(r) \neq \varphi(r')$ as $\varphi$ is an injection.

	Since $\gamma_r \subseteq \gamma_{r'}$, then $\gamma_r \cap \gamma_{r'} = \gamma_r$.
	We know $p \in \gamma_r$ and $\gamma_{r'} \iff p \in \Gamma_{\varphi(r)}$ and $\Gamma_{\varphi(r')} \iff p \in \Gamma_{\lambda \varphi(r) + (1-\lambda) \varphi(r')}$ for all $\lambda \in [0,1]$ by elicitability of $\Gamma$ and closure of subgradient sets of $G_{\Gamma}$.
	Since the reals are (uncountably) infinite, we then contradict the finiteness of $\gamma$.
	Therefore, we conclude $\gamma$ must be nonredundant.
	\jessie{This gets at the idea, but I don't think it's correct.  It also might rely on convexity of $\R$, which we may not always have, although I'd be ok with assuming it, otherwise embedding is kind of pointless.}
